The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study

### 2022-02-15 paper.tex
update

 Followed by the forward shock is a turbulent and high temperature ($\sim2$ keV) plasma.\
 By observing X-ray absorption lines through the hot\
 gaseous halo along many different sight lines in the sky, Miller& Bregman (2012)\
 found that the ratio between O viii and O vii\
 column densities is enhanced for sight lines that pass through\
 the Fermi bubbles, indicating gas temperature of a few times keV\
 inside the bubbles.

>>>>

 Followed by the forward shock is a turbulent and high temperature ($\sim2$ keV) plasma.\
 By observing X-ray absorption lines through the hot\
 gaseous halo along many different sight lines in the sky, Miller\& Bregman (2012)\
 found that the ratio between O viii and O vii\
 column densities is enhanced for sight lines that pass through\
 the Fermi bubbles, indicating gas temperature of a few times keV\
 inside the bubbles.
